Transforming Trash as an Artistic Act

### 2016-01-08 chapter4_reduced.tex
adding missing parts
Former-commit-id: 39df71832a3bfe85638abe835222f964c95f8651

% Rubbish Theory showing off.

@@

Beyond all of these for the audience the story of the collected materials is a mystery. Audience are not aware from all of these written in this thesis. I want to reveal the act behind these notebooks. However there is a lot information that can not be fit into the pages of notebooks. For that reason such problems was clearly solved through a website that store the records of notebooks and collected materials. They can visit there anytime. The other other reason that I select to website is I am comfortably and confidently fluent in coding and web development.

@@

% TODO burada bir isim uydurmak gerekli.
\textbf{Dada.} For some of the notebooks it is not obvious to name them. At this point approach of Kurt Schwitters provide me a way. He created his frequently used word \quotes{Merz} from an advertisement. It is a nonsense word and used it most of his works. I followed what he did and generated a word from a paper. I use this word for the ones the story of them are not obvious and significant.

>>>>

% TODO Rubbish Theory showing off.

@@

Beyond all of these for the audience the story of the collected materials is a mystery. Audience are not aware from all of these written in this thesis. I want to reveal the act behind these notebooks. However there is a lot information that can not be fit into the pages of notebooks. For that reason such problems can be clearly solved through a website that store the records of notebooks and collected materials. People can visit the website anytime. Further I am comfortably and confidently fluent in coding and web development. Therefore it is more appropriate for the scope of this thesis.

Notebooks will be given away. They will continue to flow between people. There is a possibility that notebooks can be trashed again. However vice verse is possible. In other words they might turn to durable objects as mentioned in Rubbish Theory. At this time, decision belongs to people. However website serve great functionality here. While the notebooks have potentials to be rubbish, records of them in the website are preserved.

@@

% TODO burada bir isim uydurmak gerekli.
\textbf{Daro.} For some of the notebooks it is not obvious to name them. At this point approach of Kurt Schwitters provides me a way. He generated his frequently used word \quotes{Merz} from an advertisement. It is a nonsense word and used in most of his works. I followed what he did and generated a word from the papers that used inside of the notebooks. I use the word \quotes{Daro} extracted from \quotes{Vardaroma Dondurmacısı} for the ones whose story are not obvious and significant.
